Old is Still Gold: A Comparison of Cyber and Regular Consumer Fraud in The United States

### 2017-01-18 paper/paper.tex
abstract

While cybercrime is a relatively recent human invention, fraudulent activity has a much longer history. This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud. We study the difference in fraud trends across time, location, ethnic and socio-economic factors. 
Both categories of frauds experience an overall decrease during the holiday season. Individuals who are victimized via traditional methods are more likely to complain using phone or in-person, while a majority of cyber victims submit fraud complaints online. By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their operational methodologies to execute scams on the Internet that were initially perpetrated through traditional means.

 \ck{ADD QUICK AND EASY CONCLUSIONS HERE}.

@@

\begin{itemize}
\vspace{8pt}
  \item Population density per zip code
  \item Education and income data \footnote{We obtained education data was obtained from \cite{zipatlas}.}
  \item Age statistics
  \item Race and ethnic information
  \vspace{8pt}
\end{itemize}

@@

\section{Evaluation}\label{eval}

>>>>

While cybercrime is a relatively recent human invention, fraudulent activity has a much longer history. This paper investigates the differences in fraud reporting and targeting among United States based consumers by comparing fraudulent activity mediated by the Internet, with traditional forms of fraud. We summarize the difference in fraud trends across time, distance and location metrics as well as ethnic and socio-economic factors. Both categories of frauds experience an overall decrease during the holiday season. Individuals who are victimized via traditional methods are more likely to complain using traditional methods, while a majority of cyber victims submit fraud complaints online. By evaluating the top frauds in each category, we demonstrate how traditional fraudsters have evolved in their methodologies execute scams on the Internet that were initially perpetrated through traditional means. Finally, based on our findings, we suggest policy based insights to strategically prevent these fraudulent activities

@@

\begin{itemize}
\vspace{8pt}
  \item Population density per zip code
  \item Education and income data \footnote{We obtained education data from \cite{zipatlas}.}
  \item Age statistics
  \item Race and ethnic information
  \vspace{8pt}
\end{itemize}

@@

\section{Hypotheses and Evaluation}\label{eval}
